Who Cares about Morality

### 2023-02-05 drafting_results_section.Rmd
added plots

We conducted a linear-mixed-effects model to test for gender differences in internalization when participants are nested within country. Our outcome measure was internalization and our predictor variable was binary gender (coded as 0 = *male*; 1 = *female*); we allowed intercepts to vary by country.
Overall, the model significantly predicted internalization, and provided a better fit for the data than the baseline model,
$\chi$^2^(`r results_anova$Df[2]`) = `r sprintf("%.2f",results_anova$Chisq[2])`), *p* `r paste(p_report(p1))`. 
There was a significant main effect for gender,
*F*(`r aov1$NumDF[1]`, `r sprintf("%.2f",round(aov1$DenDF[1],digits=2))`) = 
`r sprintf("%.2f",f3a)`, *p* `r paste(p_report(p3a))`;
with a significant positive association between being female and higher internalization scores, $b$ = `r sprintf("%.2f",results_coef$Estimate[2])`,
*t*(`r sprintf("%.2f",results_coef$df[2])`) = 
`r sprintf("%.2f",t1)`
, *p* `r paste(p_report(p2))`.
We conducted a series of independent-samples t-tests to test for gender differences in internalization across all countries. We found this effect across `r total_sig` countries (see Supplementary Materials Table S_X).

@@

We conducted another linear-mixed-effects model to test for gender differences in symbolization when participants are nested within country. Our outcome measure was symbolization and our predictor variable was binary gender (coded as 0 = *male*; 1 = *female*); we allowed intercepts to vary by country.
Overall, the model significantly predicted symbolization, and provided a better fit for the data than the baseline model,
$\chi$^2^(`r results_anova$Df[2]`) = `r sprintf("%.2f",results_anova$Chisq[2])`), *p* `r paste(p_report(p1))`. 
There was a significant main effect for gender,
*F*(`r aov1$NumDF[1]`, `r sprintf("%.2f",round(aov1$DenDF[1],digits=2))`) = 
`r sprintf("%.2f",f3a)`, *p* `r paste(p_report(p3a))`;
with a significant positive association between being female and higher symbolization scores, $b$ = `r sprintf("%.2f",results_coef$Estimate[2])`,
*t*(`r sprintf("%.2f",results_coef$df[2])`) = 
`r sprintf("%.2f",t1)`
, *p* `r paste(p_report(p2))`.
We conducted a series of independent-samples t-tests to test for gender differences in symbolization across all countries. We found this effect across `r total_sig` countries (see Supplementary Materials Table S_X).

@@

### symb

# Predictors (Individual Level Only)

## Internalization
```{r}
x <- df[which(df$sex3=="male"|df$sex3=="female"),]
x$sex3 <- droplevels(x$sex3)

```{r, include=TRUE, echo=TRUE}

model1 <- lmerTest::lmer(moral_identity_internal ~
                    sex3
                 # * age
                  + (1|country)
                , data = x
                , contrasts = list(sex3 = contr.sum, valence = contr.sum )
            )
summary(model1)
anova(model1)

## Symbolization
```{r}
x <- df[which(df$sex3=="male"|df$sex3=="female"),]
x$sex3 <- droplevels(x$sex3)
```

```{r, include=TRUE, echo=TRUE}

model1 <- lmerTest::lmer(moral_identity_symbolic ~
                    sex3
                  * age
                  + (1|country)
                , data = x
                , contrasts = list(sex3 = contr.sum, valence = contr.sum )
            )
summary(model1)
anova(model1)

# Predictors (Cultural Variables Included)

## Internalization
```{r}
x <- df[which(df$sex3=="male"|df$sex3=="female"),]
x$sex3 <- droplevels(x$sex3)
```

```{r, include=TRUE, echo=TRUE}

model1 <- lmerTest::lmer(moral_identity_internal ~
                    sex3
                    * (age
                    + Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    + Long.Term.Orientation
                    + Indulgence
                    + CTL_C
                    + CTL_DS
                    + CTL_DG)
                  + (1|country)
                , data = x
                , contrasts = list(sex3 = contr.sum, valence = contr.sum )
            )
summary(model1)
anova(model1)

#### (Regular Regression)

We also ran a regression without allowing slopes to vary by country. Results are below:

```{r, include=TRUE, echo=TRUE}

fit <- lm(moral_identity_internal ~
                    sex3
                    + age
                    + Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    + Long.Term.Orientation
                    + Indulgence
                    + CTL_C
                    + CTL_DS
                    + CTL_DG
                , data = x
            )

summary(fit)

## Symbolization
```{r}
x <- df[which(df$sex3=="male"|df$sex3=="female"),]
x$sex3 <- droplevels(x$sex3)
```

```{r, include=TRUE, echo=TRUE}

model1 <- lmerTest::lmer(moral_identity_symbolic ~
                    sex3
                    * (age
                    + Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    + Long.Term.Orientation
                    + Indulgence
                    + CTL_C
                    + CTL_DS
                    + CTL_DG)
                  + (1|country)
                , data = x
                , contrasts = list(sex3 = contr.sum, valence = contr.sum )
            )
summary(model1)
anova(model1)

#### (Regular Regression)

We also ran a regression without allowing slopes to vary by country. Results are below:

```{r, include=TRUE, echo=TRUE}

fit <- lm(moral_identity_symbolic ~
                    sex3
                    + age
                    + Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    + Long.Term.Orientation
                    + Indulgence
                    + CTL_C
                    + CTL_DS
                    + CTL_DG
                , data = x
            )

summary(fit)

# Men and Women Separately

## Men
### Internalization
```{r}
x <- df[
  which(
    df$sex3=="male"
        # |
        #   df$sex3=="female"
          ),]

x$sex3 <- droplevels(x$sex3)
```

```{r, include=TRUE, echo=TRUE}

model1 <- lmerTest::lmer(moral_identity_internal ~
                    age
                    + Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    + Long.Term.Orientation
                    + Indulgence
                    + CTL_C
                    + CTL_DS
                    + CTL_DG
                  + (1|country)
                , data = x
                , contrasts = list(sex3 = contr.sum, valence = contr.sum )
            )
summary(model1)
anova(model1)
```

#### (Regular Regression)

We also ran a regression without allowing slopes to vary by country. Results are below:

```{r, include=TRUE, echo=TRUE}

fit <- lm(moral_identity_internal ~
                    age
                    + Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    + Long.Term.Orientation
                    + Indulgence
                    + CTL_C
                    + CTL_DS
                    + CTL_DG
                , data = x
            )

summary(fit)

### Symbolization
```{r}
x <- df[
  which(
    df$sex3=="male"
        # |
        #   df$sex3=="female"
          ),]

x$sex3 <- droplevels(x$sex3)
```

```{r, include=TRUE, echo=TRUE}

model1 <- lmerTest::lmer(moral_identity_symbolic ~
                    age
                    + Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    + Long.Term.Orientation
                    + Indulgence
                    + CTL_C
                    + CTL_DS
                    + CTL_DG
                  + (1|country)
                , data = x
                , contrasts = list(sex3 = contr.sum, valence = contr.sum )
            )
summary(model1)
anova(model1)
```

#### (Regular Regression)

We also ran a regression without allowing slopes to vary by country. Results are below:

```{r, include=TRUE, echo=TRUE}

fit <- lm(moral_identity_symbolic ~
                    age
                    + Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    + Long.Term.Orientation
                    + Indulgence
                    + CTL_C
                    + CTL_DS
                    + CTL_DG
                , data = x
            )

summary(fit)

## Women
### Internalization

```{r}
x <- df[
  which(
    # df$sex3=="male"
    #     |
          df$sex3=="female"
          ),]

x$sex3 <- droplevels(x$sex3)
```

```{r, include=TRUE, echo=TRUE}

model1 <- lmerTest::lmer(moral_identity_internal ~
                    age
                    + Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    + Long.Term.Orientation
                    + Indulgence
                    + CTL_C
                    + CTL_DS
                    + CTL_DG
                  + (1|country)
                , data = x
                , contrasts = list(sex3 = contr.sum, valence = contr.sum )
            )
summary(model1)
anova(model1)

#### (Regular Regression)

We also ran a regression without allowing slopes to vary by country. Results are below:

```{r, include=TRUE, echo=TRUE}

fit <- lm(moral_identity_internal ~
                    age
                    + Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    + Long.Term.Orientation
                    + Indulgence
                    + CTL_C
                    + CTL_DS
                    + CTL_DG
                , data = x
            )

summary(fit)

### Symbolization
```{r}
x <- df[
  which(
    # df$sex3=="male"
    #     |
          df$sex3=="female"
          ),]

x$sex3 <- droplevels(x$sex3)
```

```{r, include=TRUE, echo=TRUE}

model1 <- lmerTest::lmer(moral_identity_symbolic ~
                    age
                    + Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    + Long.Term.Orientation
                    + Indulgence
                    + CTL_C
                    + CTL_DS
                    + CTL_DG
                  + (1|country)
                , data = x
                , contrasts = list(sex3 = contr.sum, valence = contr.sum )
            )
summary(model1)
anova(model1)

#### (Regular Regression)

We also ran a regression without allowing slopes to vary by country. Results are below:

```{r, include=TRUE, echo=TRUE}

fit <- lm(moral_identity_symbolic ~
                    age
                    + Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    + Long.Term.Orientation
                    + Indulgence
                    + CTL_C
                    + CTL_DS
                    + CTL_DG
                , data = x
            )

summary(fit)

>>>>

We conducted a linear-mixed-effects model to test for gender differences in internalization when participants are nested within country. Our outcome measure was internalization and our predictor variable was binary gender (coded as 0 = *male*; 1 = *female*); we allowed intercepts to vary by country.
Overall, the model significantly predicted internalization, and provided a better fit for the data than the baseline model,
$\chi$^2^(`r results_anova$Df[2]`) = `r sprintf("%.2f",results_anova$Chisq[2])`, *p* `r paste(p_report(p1))`. 
There was a significant main effect for gender,
*F*(`r aov1$NumDF[1]`, `r sprintf("%.2f",round(aov1$DenDF[1],digits=2))`) = 
`r sprintf("%.2f",f3a)`, *p* `r paste(p_report(p3a))`;
with a significant positive association between being female and higher internalization scores, $b$ = `r sprintf("%.2f",results_coef$Estimate[2])`,
*t*(`r sprintf("%.2f",results_coef$df[2])`) = 
`r sprintf("%.2f",t1)`
, *p* `r paste(p_report(p2))`.
We conducted a series of independent-samples t-tests to test for gender differences in internalization across all countries. We found this effect across `r total_sig` countries (see Supplementary Materials Table S_X).

@@

We conducted another linear-mixed-effects model to test for gender differences in symbolization when participants are nested within country. Our outcome measure was symbolization and our predictor variable was binary gender (coded as 0 = *male*; 1 = *female*); we allowed intercepts to vary by country.
Overall, the model significantly predicted symbolization, and provided a better fit for the data than the baseline model,
$\chi$^2^(`r results_anova$Df[2]`) = `r sprintf("%.2f",results_anova$Chisq[2])`, *p* `r paste(p_report(p1))`. 
There was a significant main effect for gender,
*F*(`r aov1$NumDF[1]`, `r sprintf("%.2f",round(aov1$DenDF[1],digits=2))`) = 
`r sprintf("%.2f",f3a)`, *p* `r paste(p_report(p3a))`;
with a significant positive association between being female and higher symbolization scores, $b$ = `r sprintf("%.2f",results_coef$Estimate[2])`,
*t*(`r sprintf("%.2f",results_coef$df[2])`) = 
`r sprintf("%.2f",t1)`
, *p* `r paste(p_report(p2))`.
We conducted a series of independent-samples t-tests to test for gender differences in symbolization across all countries. We found this effect across `r total_sig` countries (see Supplementary Materials Table S_X).

@@
